\documentclass[11pt]{article}
%Gummi|065|=)
\title{\textbf{Features}}
\author{}
\date{}
\begin{document}

\maketitle

\section{Sign-Up/Log-In}

A feature which allows the user to sign up using name, email and a password. If user is already registered on the application, then he/she can sign in using email and password. In case the user has forgotten the password, there is an option for resetting it via email.

\section{Entry/Image Form}
An entry form accessed via the 'Hearth' button on the menu-bar. It provides a title, an entry field and an image upload option. The title bar has a not\_empty validator to ensure non-garbage values. 

\section{Entries Display - List and Individual}
List of entries with images accessed via the 'Memory' button on the menu-bar. It has options to search for specific names, and against each entry name, there are options for viewing, editing and deleting the specific entry. Clicking on the View Button enables a display screen for each entry.

\section{Event Form}
Another input form for the events, accessed via the 'Event' button the menu-bar with the input fields consisting of date and time pop-ups when selected for easier ease of inputs. Also contains name and description of event. 

\section{Events Display - List and Individual}
 Selected via the 'Timeline' button on the menu-bar, this displays a list of all stored events in the application's database. The list has options to search for specific names, and against each entry name, there are options for viewing, editing and deleting the specific entry. Clicking on the View Button enables a display screen for each entry.
 
 \section{Privacy}
Each user can access only his or her events and entries via this application when they are logged in, hereby maintaining the privacy of the individual's data.

\section{Upload Image; Search, View, Edit, Delete Entries }
As mentioned earlier, the application allows users to upload their pictures online onto the app, and also allows the options of searching, viweing, editing, and deleting the app's entries and events. 

 
 
\end{document}